Lit Review Figure

### 2017-09-15 code/Lit_Review_Figure.Rmd
changed order of plots
cleaned up the figure page; keeping it as html instead of nb.html because the interactive block label character length is breaking the nb html.

---
title: 'Lit Review Figure'
output: html_document
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(rmarkdown)
library(stringr)
library(plotly)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
options(scipen = 1, digits = 4)
```

Read data in

```{r}
fig_data <- read.csv('/Users/zeynepenkavi/Downloads/lit_review_figure.csv')
```

@@

```{r warning= FALSE, message =FALSE, fig.height=36}
fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()
```

```{r warning=FALSE, message=FALSE, fig.height=36}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()+
  theme(legend.position="none"),
tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
  layout(showlegend=FALSE)
```

>>>>

---
title: "Lit Review Figure"
output:
  html_document: default
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(stringr)
library(plotly)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
options(scipen = 1, digits = 4)
```

```{r echo=FALSE}
fig_data <- read.csv('/Users/zeynepenkavi/Downloads/lit_review_figure.csv')
```

```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()+
  theme(legend.position="none"),
tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
  layout(showlegend=FALSE)
```

@@

```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE}
fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()
```
